Conversations in time: interactive visualisation to explore structured temporal data

### 2020-09-03 tsibbletalk.Rmd
openning paragraph for slicing time

@@

The other critical aspect of a tsibble is "index", that provides foundational temporal context. A common tool in time series analytical toolkit is seasonal plots that lay time series not on the whole time scale, but on an origin-less relative time unit, for example `gg_season()` in the {feasts} package. It helps to examine and emphasise periodic/aperiodic patterns, comparing to time series plots that primarily focus on trends. Standard seasonal plots break the overall time into two components: seasonal periods on the x-axis, and grouped by their corresponding lower-resolution time. For example, monthly data can be decomposed into months separated by years, and hourly data into hours grouped by days. Data collected at lower-level resolutions often exhibits more than one seasonal patterns. To discover typical seasonal or non-typical profiles, it is helpful to quickly browse through many possible periods. Interactivity ought to be enabled.

>>>>

The shared tsibble data leverages the `key` attribute to converse with many coordinated views, with or without \CRANpkg{shiny}. On the other hand, a second critical attribute--`index`--lays the foundational temporal context that augments the conversation. When temporal data are plotted and stretched against the entire span like Figure \ref{fig:highlight-retail-1}, it puts the emphasis on the trend. When the data are wrapped over origin-less time units, such as one or two quarters, it makes seasonal patterns more pronounced. The \CRANpkg{tsibbletalk} package provides a shiny module

@@

Standard seasonal plots break the overall time into two components: seasonal periods on the x-axis, and grouped by their corresponding lower-resolution time. For example, monthly data can be decomposed into months separated by years, and hourly data into hours grouped by days. Data collected at lower-level resolutions often exhibits more than one seasonal patterns. To discover typical seasonal or non-typical profiles, it is helpful to quickly browse through many possible periods. Interactivity ought to be enabled.

### 2020-09-03 tsibbletalk.tex
openning paragraph for slicing time

@@

The other critical aspect of a tsibble is ``index'', that provides
foundational temporal context. A common tool in time series analytical
toolkit is seasonal plots that lay time series not on the whole time
scale, but on an origin-less relative time unit, for example
\texttt{gg\_season()} in the \{feasts\} package. It helps to examine and
emphasise periodic/aperiodic patterns, comparing to time series plots
that primarily focus on trends. Standard seasonal plots break the
overall time into two components: seasonal periods on the x-axis, and
grouped by their corresponding lower-resolution time. For example,
monthly data can be decomposed into months separated by years, and
hourly data into hours grouped by days. Data collected at lower-level
resolutions often exhibits more than one seasonal patterns. To discover
typical seasonal or non-typical profiles, it is helpful to quickly
browse through many possible periods. Interactivity ought to be enabled.

>>>>

The shared tsibble data leverages the \texttt{key} attribute to converse
with many coordinated views, with or without \CRANpkg{shiny}. On the
other hand, a second critical attribute--\texttt{index}--lays the
foundational temporal context that augments the conversation. When
temporal data are plotted and stretched against the entire span like
Figure \ref{fig:highlight-retail-1}, it puts the emphasis on the trend.
When the data are wrapped over origin-less time units, such as one or
two quarters, it makes seasonal patterns more pronounced. The
\CRANpkg{tsibbletalk} package provides a shiny module

@@

Standard seasonal plots break the overall time into two components:
seasonal periods on the x-axis, and grouped by their corresponding
lower-resolution time. For example, monthly data can be decomposed into
months separated by years, and hourly data into hours grouped by days.
Data collected at lower-level resolutions often exhibits more than one
seasonal patterns. To discover typical seasonal or non-typical profiles,
it is helpful to quickly browse through many possible periods.
Interactivity ought to be enabled.
